\thetitle

### 2021-04-30 writing/mutate-benchmarks-figure.tex
uniform editorial voice, mistakes, typos, size of text in figures, captions
Clean up the two tables (figs 4 and 5)

\begin{figure*}
\begin{tabular}{p{1.4cm} | p{6.9cm} | p{2.0cm} | r | r}
             {\bf  name} & {\bf description} & {\bf author} & {\bf loc} & {\bf mod.} \\ \hline
%% ---------------------------------------------------------------------------------------------------------------

@@

\texttt{take5} & Mixin-based card game simulator & M.Felleisen & 465 & 8\\ \hline

\texttt{tetris} & Functional implementation of Tetris & D. Van Horn &   280 & 9 \\ \hline

\texttt{suffix\-tree} & algorithm for common longest subsequences between strings. & D. Yoo & 1500 & 6 \\

@@

\caption{Benchmarks summary.} \label{table:benchmark-descriptions}

>>>>

\begin{figure*} \footnotesize
\begin{tabular}{p{1.5cm} | p{6.9cm} | p{1.9cm} | r | r}
             {\bf  name} & {\bf description} & {\bf author} & {\bf loc} & {\bf mod.} \\ \hline
%% ---------------------------------------------------------------------------------------------------------------

@@

\texttt{take5} & mixin-based card game simulator & M.Felleisen & 465 & 8\\ \hline

\texttt{tetris} & functional implementation of Tetris & D. Van Horn &   280 & 9 \\ \hline

\texttt{suffix\-tree} & algorithm for common longest subsequences between strings & D. Yoo & 1500 & 6 \\

@@

\caption{Summary of benchmarks} \label{table:benchmark-descriptions}
